CROCUS: Crowd Counting Using Smartphones

### 2019-05-24 cysep-eurosp/abstract.tex

\textbf{Approach:}
 In this paper we propose CROCUS, a decentralized system based on
 smartphones that combines anonymous credentials, witnesses of
 proximity, and storage of participation proofs on a public ledger
 (e.g., blockchain) to achieve properties similar to those needed for
 electronic voting, where, put simply, it is important to count
 everyone, but only once, not leak private information, and be able to
 prove that the count was done correctly.

\textbf{More detailed approach:} 
By running a distance bounding scheme with anonymous credentials,
physically present persons (such as protest participants) and create proof
shares. This is done using smartphones with (assumed)
distance-bounding chips, without Internet connection but using any
available local communications. Before and after the event (protest), participants (and
witnesses), interact with a public ledger such as a blockchain (which does require
Internet access, and anonymization by e.g. Tor). Before the event to get
a timestamp and after the event to upload proof shares, again with a
time stamp. The proof shares form verifiable yet privacy-preserving
participation proofs according to counting eligibility criteria. These criteria, including
time interval, location range, number or kind (e.g., anyone, trusted
journalists) of unique proof shares
needed for a proof, enable verification by recount. Counting is done
by downloading the proof shares from the ledger, checking the validity
and eligibility, and summing up. Any published counts need to also
publish the criteria used to be verified, but anyone could decide on
their own criteria and count accordingly.

>>>>

\textbf{Approach:}
In this paper we propose CROCUS, a decentralized system based on
smartphones that combines anonymous credentials, witnesses of
proximity, and storage of participation proofs on a public ledger
(e.g., blockchain).
CROCUS achieves properties similar to those needed for
electronic voting, where, put simply, it is important to count
everyone, but only once, not leak private information, and be able to
prove that the count was done correctly.

\textbf{More detailed approach:} 
By running a distance bounding scheme with anonymous credentials,
physically present persons (such as protest participants) create proof
shares. This is done using smartphones with (assumed)
distance-bounding chips, without Internet connection but using any
available local communications. Before and after the event (protest), participants (and
witnesses) interact with a public ledger such as a blockchain (which does require
Internet access, and anonymization by e.g. Tor). Before the event to get
a timestamp and after the event to upload proof shares, again with a
time stamp. The proof shares form verifiable yet privacy-preserving
participation proofs according to counting eligibility criteria. These criteria, including
time interval, location range, number or kind (e.g., anyone, trusted
journalists) of unique proof shares
needed for a proof, enable verification by recount. Counting is done
by downloading the proof shares from the ledger, checking the validity
and eligibility, and summing up. Any published counts need to also
publish the criteria used to be verified, but anyone could decide on
their own criteria and count accordingly.
